\Large \bf Uncovering Distributed System Bugs during Testing (not Production!)

### 2015-09-20 evaluation.tex
updates in case studies

For the vNext case study, the random scheduler was able to reproduce the bug in less than 10 seconds. The reason that the number of scheduling steps to find the bug is much higher than the rest of the bugs in the table is that this bug is a liveness violation: as discussed in Section~\ref{sec:psharp:testing} we leave the program to run for a long time before checking if the liveness property holds. The PCT scheduler was unable to find the bug using the bug depth of 2, which suggests that the bug requires a larger depth bound to be found.

>>>>

For the vNext case study, the random scheduler was able to reproduce the bug in less than 10 seconds. The reason that the number of scheduling steps to find the bug is much higher than the rest of the bugs in the table is that this bug is a liveness violation: as discussed in \S\ref{sec:psharp:testing} we leave the program to run for a long time before checking if the liveness property holds. The PCT scheduler was unable to find the bug using the bug depth of 2, which suggests that the bug requires a larger depth bound to be found.

### 2015-09-20 experience.tex
updates in case studies

The Live Azure Table Migration (MigratingTable) is a library for
\emph{transparently migrating} a data set between tables in an Azure Storage
service \emph{while} an application is accessing this data set. This case study
is interesting because its developers built the \psharp model of the system
while developing the library to increase confidence in its implementation;
indeed they discovered many bugs during this \emph{co-development} process.
Another interesting aspect of this system is that it heavily
uses the \texttt{async}/\texttt{await} primitives, which were not supported in
the original \psharp runtime, and thus required us to extend \psharp with
support for intra-machine concurrency (see Section~\ref{sec:psharp:async}). Finally, multiple 
complex safety properties were written to test MigratingTable with \psharp, 
whereas the vNext model focused on a single liveness property.

@@

%We wanted to implement the core MigratingTable algorithms in \csharp ``async/await'' code, like most of Artifact Services, to achieve both good readability and good performance.  We used a method similar to that described in Section~\ref{sec:psharp:async} to bring the generated TPL tasks under the control of the \psharp scheduler.  Then we implemented an ``async'' RPC mechanism based on the .NET RealProxy class that automates the generation of proxies for objects hosted by other \psharp machines (in our setting, the service machines use proxies for the \texttt{SpecTable}s and various auxiliary objects hosted by the tables machine).  When a machine calls a method on a proxy, the proxy sends a \psharp message to the host machine, causing it to execute the method call on the original object and send back the result, which the proxy then returns.  Thus, the use of these proxies as \texttt{IChainTable} backends is transparent to the MigratingTable library, thanks to dynamic dispatch.

>>>>

The Live Azure Table Migration (MigratingTable) is a library for \emph{transparently migrating} a data set between tables in an Azure Storage service \emph{while} an application is accessing this data set. This case study is particularly interesting because its developers \emph{co-developed} the system with its \psharp model to increase confidence in the former's implementation. Indeed, this co-development process resulted in many tricky bugs discovered before the system went into production (see \S\ref{sec:eval}). The MigratingTable modeling effort differs from the vNext case study: the vNext developers focused on specifying a single liveness property; whereas the MigratingTable developers had to write many complex safety properties. MigratingTable is also interesting because it heavily uses the \texttt{async} and \texttt{await} \csharp 5.0 primitives, which were not originally supported in \psharp. To be able to test MigratingTable, as well as other systems written in \csharp 5.0, we had to extend \psharp with support for intra-machine concurrency (see \S\ref{sec:psharp:testing}).

@@

%We wanted to implement the core MigratingTable algorithms in \csharp ``async/await'' code, like most of Artifact Services, to achieve both good readability and good performance.  We used a method similar to that described in \S\ref{sec:psharp:async} to bring the generated TPL tasks under the control of the \psharp scheduler.  Then we implemented an ``async'' RPC mechanism based on the .NET RealProxy class that automates the generation of proxies for objects hosted by other \psharp machines (in our setting, the service machines use proxies for the \texttt{SpecTable}s and various auxiliary objects hosted by the tables machine).  When a machine calls a method on a proxy, the proxy sends a \psharp message to the host machine, causing it to execute the method call on the original object and send back the result, which the proxy then returns.  Thus, the use of these proxies as \texttt{IChainTable} backends is transparent to the MigratingTable library, thanks to dynamic dispatch.

### 2015-09-20 methodology.tex
updates in case studies

%A typical wrapper machine contains a handle (as a field) to the system component that is being wrapped (in our case the real Extent Manager object) and the event handlers are responsible for translating any received events to method calls in the real code that is being tested. The \texttt{ExtentManager} is accompanied by a mocked version of the real Network Engine class. The real Extent Manager is communicating with the outside world via remote procedure calls, but in \psharp harness we want to capture this communicating and expose it as calls to \psharp communicating primitives. This is discussed in detail in Section~\ref{sec:method:model:dispath}.

%As shown in Figure~\ref{fig:wrap_target}, the \texttt{ExtentManagerMachine} is a wrapper machine and is used to connect the \psharp modeled code with the legacy \csharp code. A typical wrapper machine contains a handle (as a field) to the system component that is being wrapped (in our case the real Extent Manager object) and the event handlers are responsible for translating any received events to method calls in the real code that is being tested. The \texttt{ExtentManager} is accompanied by a mocked version of the real Network Engine class. The real Extent Manager is communicating with the outside world via remote procedure calls, but in \psharp harness we want to capture this communicating and expose it as calls to \psharp communicating primitives. This is discussed in detail in Section~\ref{sec:method:model:dispath}.

@@

\texttt{RepairMonitor} is a liveness monitor machine (see Section~\ref{sec:bg:bugs}) that transitions between a cold and a hot state. Whenever an extent node fails, \texttt{RepairMonitor} is notified. As soon as the number of extent replicas falls below a specified target (three replicas in the current test harness), \texttt{RepairMonitor} transitions into the hot \emph{repairing} state, where the missing replica is being repaired. Whenever a replica is repaired, the \texttt{RepairMonitor} machine is also notified. It transitions into the cold \emph{repaired} state, when the replica number reaches again the target, as illustrated in Figure~\ref{fig:monitor}.

@@

It took less than ten seconds for the \psharp testing engine to report the first occurrence of a liveness bug in vNext (see Section~\ref{sec:eval}). Upon examining the debug trace, the vNext developers were able to confirm the bug.

@@

%Finally, the \texttt{Timer} machine models the operating system timer and is responsible for triggering events related to the Azure Storage vNext logic (e.g. synchronization messages, heartbeats and repair logic loops). This is discussed in detail in Section~\ref{sec:method:model:timers}.

>>>>

%A typical wrapper machine contains a handle (as a field) to the system component that is being wrapped (in our case the real Extent Manager object) and the event handlers are responsible for translating any received events to method calls in the real code that is being tested. The \texttt{ExtentManager} is accompanied by a mocked version of the real Network Engine class. The real Extent Manager is communicating with the outside world via remote procedure calls, but in \psharp harness we want to capture this communicating and expose it as calls to \psharp communicating primitives. This is discussed in detail in \S\ref{sec:method:model:dispath}.

%As shown in Figure~\ref{fig:wrap_target}, the \texttt{ExtentManagerMachine} is a wrapper machine and is used to connect the \psharp modeled code with the legacy \csharp code. A typical wrapper machine contains a handle (as a field) to the system component that is being wrapped (in our case the real Extent Manager object) and the event handlers are responsible for translating any received events to method calls in the real code that is being tested. The \texttt{ExtentManager} is accompanied by a mocked version of the real Network Engine class. The real Extent Manager is communicating with the outside world via remote procedure calls, but in \psharp harness we want to capture this communicating and expose it as calls to \psharp communicating primitives. This is discussed in detail in \S\ref{sec:method:model:dispath}.

@@

\texttt{RepairMonitor} is a \psharp liveness monitor machine (see \S\ref{sec:bg:bugs}) that transitions between a cold and a hot state. Whenever an extent node fails, \texttt{RepairMonitor} is notified. As soon as the number of extent replicas falls below a specified target (three replicas in the current test harness), \texttt{RepairMonitor} transitions into the hot \emph{repairing} state, where the missing replica is being repaired. Whenever a replica is repaired, the \texttt{RepairMonitor} machine is also notified. It transitions into the cold \emph{repaired} state, when the replica number reaches again the target, as illustrated in Figure~\ref{fig:monitor}.

@@

It took less than ten seconds for the \psharp testing engine to report the first occurrence of a liveness bug in vNext (see \S\ref{sec:eval}). Upon examining the debug trace, the developers of vNext were able to quickly confirm the bug.

@@

%Finally, the \texttt{Timer} machine models the operating system timer and is responsible for triggering events related to the Azure Storage vNext logic (e.g. synchronization messages, heartbeats and repair logic loops). This is discussed in detail in \S\ref{sec:method:model:timers}.

### 2015-09-20 overview.tex
updates in case studies

Our approach of using \psharp to test distributed systems, implemented in .NET, requires the developer to perform the following three key modeling tasks. These tasks are illustrated in Section~\ref{sec:method} using the Azure Storage vNext as a running example.

@@

The \psharp runtime is a lightweight layer build on top of the Task Parallel Library (TPL) of .NET that implements the semantics of \psharp: creating state machines, executing them concurrently using the default task scheduler of TPL, and sending events and enqueueing them in the appropriate machines. A key capability of the \psharp runtime is that it can execute in \emph{bug-finding} mode, which systematically tests a \psharp program to find bugs using the safety and liveness monitors that were discussed in Section~\ref{sec:bg:bugs}.

@@

\textbf{Handling \csharp 5.0 asynchrony}.
The Live Azure Table Migration system (see Section~\ref{sec:cases:migration}) heavily uses the \texttt{async} and \texttt{await} \csharp 5.0 language primitives. An \texttt{async} method is able to perform \texttt{await} on a TPL task \emph{without} blocking the current thread. The \csharp compiler achieves this non-blocking behavior by wrapping the code following an \texttt{await} statement in an internal TPL \emph{task continuation}, and returning execution to the caller of the \texttt{async} method. The TPL scheduler executes this task continuation when the task being awaited has completed. In principle, this asynchrony can be modeled using the \psharp primitives for machine creation and message passing. However, in our experience, modeling async/await asynchronous code using \psharp is difficult and time consuming, and thus unlikely to scale for large code bases. To tackle this problem, we developed a solution that automatically captures asynchronously created TPL tasks and wraps them in temporary \psharp machines.

>>>>

Our approach of using \psharp to test distributed systems, implemented in .NET, requires the developer to perform the following three key modeling tasks. These tasks are illustrated in \S\ref{sec:method} using the Azure Storage vNext as a running example.

@@

The \psharp runtime is a lightweight layer build on top of the Task Parallel Library (TPL) of .NET that implements the semantics of \psharp: creating state machines, executing them concurrently using the default task scheduler of TPL, and sending events and enqueueing them in the appropriate machines. A key capability of the \psharp runtime is that it can execute in \emph{bug-finding} mode, which systematically tests a \psharp program to find bugs using the safety and liveness monitors that were discussed in \S\ref{sec:bg:bugs}.

@@

\textbf{Handling \csharp 5.0 asynchrony}.
The Live Azure Table Migration system (see \S\ref{sec:cases:migration}) heavily uses the \texttt{async} and \texttt{await} \csharp 5.0 language primitives. An \texttt{async} method is able to perform \texttt{await} on a TPL task \emph{without} blocking the current thread. The \csharp compiler achieves this non-blocking behavior by wrapping the code following an \texttt{await} statement in a TPL \emph{task continuation}, and then returning execution to the caller of the \texttt{async} method. The TPL scheduler executes this task continuation when the task being awaited has completed. In principle, this asynchrony can be modeled using the \psharp primitives for machine creation and message passing. However, in our experience, modeling async/await asynchronous code using \psharp is difficult and time consuming, and thus unlikely to scale for large code bases. To tackle this problem, we developed a solution that automatically captures asynchronously created TPL tasks and wraps them in temporary \psharp machines.
